Maintenance planning on French military aircraft operations

### 2018-09-19 R/presentations/CLAIO_presentation/presentation.Rmd
updated CLAIO ppt with statistics on results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
source('diagrams/fixed_interval.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 15, width='100%')
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
task_gantt <- tasks_gantt()
task_employees <- tasks_employees()
```

@@

<!-- ## Model: minimum assignment times -->

<!-- <!-- <div class="incremental"> -->

<!-- \begin{align} -->
<!--     & a^s_{jti} \geq a_{jti} - a_{j(t-1)i} -->
<!--             & t =1, ..., \mathcal{T}, j \in \mathcal{J}_t, i \in \mathcal{I}_j \label{eq:start1} \\ -->
<!--     & a^s_{j0i} \geq a_{j0i} - 1 \!1_{i \in \mathcal{A}^{init}_{j}} -->
<!--             & j \in \mathcal{J}_0, i \in \mathcal{I}_j \label{eq:start2} \\         -->
<!--     & \sum_{t' \in \mathcal{T}^{MT}_{jt}} a^s_{jt'i} \leq a_{jti}  -->
<!--     & j \in \mathcal{J}, t \in \mathcal{T}_j, i \in \mathcal{I}_j \label{eq:start3} -->
<!-- \end{align} -->

<!-- Each task needs a minimum continuous duration at each assignment. -->

<!-- \pause -->

@@

# Results

@@

Instances have been created with the following characteristics:

<!-- <div class="incremental"> -->

* 60 - 200 resources.
* 90 periods.
* Tasks: 3 - 9
    * 12 - 36 periods long
    * 2 - 5 resources needed

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
path_to_R_dir <- "./../../"
setwd(path_to_R_dir)
source('functions/params.R')
source('functions/import_results.R')
source('functions/scenario_analysis.R')
source('diagrams/fixed_interval.R')
all_exp_dir <- PATHS[['results']] %>% paste0('simulated_data/')
exp_directory <- all_exp_dir %>% paste0('2_task/201809180941/')
gantt <- print_solution(exp_directory, max_resources = 15, width='100%')
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
task_gantt <- tasks_gantt()
task_employees <- tasks_employees()
scen_means <- scenario_mean(all_exp_dir)
infeasible <- scenario_get_gaps(all_exp_dir) %>% lapply(function(scn){
    a <- length(scn)
    scn %>% is.na %>% sum %>% divide_by(a/100)
} )

@@

@@

# Results and perspectives

@@

Instances have been generated with the following main characteristics:

* 60 - 200 resources.
* 90 periods.
* 3 - 9 tasks:
    * 12 - 36 periods long
    * 2 - 5 resources needed

* Small instances have **30.000 variables** and **20.000 constraints**.
* Medium instances have **80.000 variables** and **50.000 constraints**.
* Runs of 30 minutes have been done on 30 randomly generated cases per scenario and they return a gap between 20% and 40% if a solution exists.
* CPLEX was used in an i7, quadcore Ubuntu 18.04 workstation.

## Statistics

* `r infeasible[1]`% of instances were proved infeasible inmediately.
* From feasible small instances, a gap of `r scen_means[1]`% was found after 30 min
* From feasible medium instances, a gap of `r scen_means[2]`% was found after 30 min.

## Perspectives

* More extreme (bigger) scenarios need to be tested: more tasks and more resources.
* A deeper analysis on the detailed solving process is envisioned. Including extending the solving time.
* Benchmarking of solvers (gurobi, CBC, choco and CPO) is work in progress. Also: heuristics.
* The inclusion of new possibilities, such as the planned storage of resources is pending.
* A stochastic sensibility analysis needs to be done, including taking account of stochasticity in the input data.
